Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-07-09 paper/paper.tex
Just work in progress

In this model, the signal transmitted when a ligand binds to a receptor on a
growth cone can lead to one of two effects; the signal may induce the growth
cone to climb the gradient of ligand expression, in which case the interaction
is \emph{attractive} or the cone may descend the gradient of ligand expression
if the interaction is \emph{repulsive}.

Based on a Michaelis-Menten model applied to
receptor-binding, \citet{mortimer_bayesian_2009} give an expression for the
probability of an individual receptor being bound as a function of the ligand
expression, $\gamma$, and the ligand gradient, $\mu$;
\begin{equation}
P(b=1|\gamma,\mu) = \frac{\gamma(1 + \mu r)}{1 + \gamma(1 + \mu r)},
\end{equation}
where $r$ is the distance of the receptor from the centre of a 1D growth
cone. To determine the sampled direction signal (for one dimension), we assume
evenly spaced receptors and sample from a uniform distribution for each
location across the growth cone.

This is where I really want to say ``the only interactions in the model are
via forward (ligand-activates-receptor) and reverse
(receptor-activates-ligand) signalling''. Something like:

Interactions in the model are by receptor-ligand interactions only. Forward
interactions are those in which the ligand activates the receptor, delivering
a signal into the receptor-expressing cell. Reverse signals occur when a
membrane-bound ligand is activated~\citep{wu_role_2019}.

>>>>

In this model, the signal transmitted when a ligand binds to a receptor on a
growth cone can lead to one of two effects; the signal may induce the growth
cone to climb the gradient of ligand expression, in which case the interaction
is \emph{attractive} or the cone may descend the gradient of ligand expression
if the interaction is \emph{repulsive}. To determine the strength of the
effect we could assume a purely linear receptor binding model, and set the
movement of the growth cone to be $\sum_i \pm r_i \times \grad l_i$. While
this approach works, it does not allow us to investigate the effect of
receptor binding noise (\textbf{FIXME}: Be sure to have included a discussion
on the three types of noise as described by Goodhill, 2016 in the
introduction) on the ability of the system to generate topographic order.

Instead, we treat the receptor binding at the growth cone with greater
care. Based on a Michaelis-Menten model applied to
receptor binding, \citet{mortimer_bayesian_2009} give an expression for the
probability of an individual receptor being bound as a function of the ligand
expression, $\gamma$, and the ligand gradient, $\mu$;
\begin{equation}
P(b=1|\gamma,\mu) = \frac{\gamma(1 + \mu r)}{1 + \gamma(1 + \mu r)},
\end{equation}
where $r$ is the distance of the receptor from the centre of a 1D growth
cone. To determine the growth cone's estimate of the gradient, we assume
evenly spaced receptors and sample from a uniform distribution for each
location across the growth cone. Activated receptors contribute

%This is where I really want to say ``the only interactions in the model are
%via forward (ligand-activates-receptor) and reverse
%(receptor-activates-ligand) signalling''. Something like:

%Interactions in the model are by receptor-ligand interactions only. Forward
%interactions are those in which the ligand activates the receptor, delivering
%a signal into the receptor-expressing cell. Reverse signals occur when a
%membrane-bound ligand is activated~\citep{wu_role_2019}.
